Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS J08354256-0819237 and 2MASS J18212815+1414010

### 2016-12-04 ms.tex
I added a clarification to the color-magnitude diagram.
I made Adam's edits the main ms.tex version.

We fit the time series of each brown dwarf in 25 spectral bins each to assess the wavelength-dependent nature of their variations.
The simple model can be described as 
\begin{equation}
F(t) = A * \sin(2 \pi (t - t_0)/\tau) + B t + C
\end{equation}
where $F$ is the flux as a function of time ($t$), A is the amplitude of the variations, $t_0$ is the time offset of the variations, $\tau$ is period of the variations and B and C are linear terms describing the baseline trend.
For the fits, we let $A$, $t_0$, $B$ and $C$ be free parameters.
We fixed the sinusoidal period $\tau$ at the literature value of rotation period (Table \ref{tab:bdProp}) because there are trends (with a period of $\sim$24 hr) due to uncorrected telluric variations that that are not relevant to the brown dwarf system.
We imposed a prior that $A \geq 0$ so that a solution with a $\pi$ phase offset and negative amplitude isn't found.

@@

Figure \ref{fig:ampSpec} shows the best fit amplitudes as a function of wavelength.
We use the standard deviation of points near minimum to estimate the noise in the flux time series.
The Levenberg-Marquardt chi-squared minimization code \texttt{mpfit} is used to fit each wavelength bin independently and propagate the errors in the flux time series to amplitude uncertainty.
The amplitude spectrum ($A$ as a function of wavelength) of 2MASS J0835, (Figure \ref{fig:ampspec0835}), shows small ($\lesssim 0.4\%$) amplitudes with a flat trend as a function of wavelength.
2MASS J1821, on the other hand, shows a clear decreasing trend as function of wavelength.
This was is the same trend observed for 2MASS J1821 by HST over a shorter wavelength range (1.1 to 1.7~$\mu$m) by \citet{yang2016exStormsBD}.
We shade the regions from 1.32 to 1.5~$\mu$m and 1.78 to 1.95~$\mu$m in Figure \ref{fig:ampSpec} because these wavelength ranges are affected by telluric water vapor absorption not fully removed by the simultaneous reference star.

@@

\section{Color-Magnitude Diagram}
\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{color_mag.pdf}
\caption{Color-Magnitude diagram from \citet{dupuy2012ltparallax}.}\label{fig:CMD}
\end{centering}
\end{figure}

>>>>

We extracted separate lightcurves for each target in 25 spectral bins of width XXX~$\mu$m, as shown in Figure~\ref{fig:tserPfold}. Each of these were fit to a simple sinusoidal model {\bf [NOTE: CHANGE TO COSINE FOR SIMPLER INTERPRETATION OF TO]}:
\begin{equation}
F(t) = A * \cos(2 \pi (t - t_0)/\tau) + B t + C
\end{equation}
Here, $F(t)$ is the flux as a function of time $t$, $A$ is the amplitude of periodic variations, $t_0$ is the time of maximum periodic flux, $\tau$ is period of the variations, and $B$ and $C$ are linear terms describing any baseline trend.
For the fits, we let $A$, $t_0$, $B$ and $C$ be free parameters, but fixed $\tau$ at the literature value of rotation period due to systematic trends (with a period of $\sim$24 hr) caused by uncorrected telluric variations.
We also imposed a prior that $A \geq 0$ so that solutions with a $\pi$ phase offset and negative amplitude were ignored.

@@

Figure \ref{fig:ampSpec} shows the best fit amplitudes as a function of wavelength.
We use the standard deviation of points near minimum to estimate the noise in the flux time series.
The Levenberg-Marquardt chi-squared minimization code \texttt{mpfit} is used to fit each wavelength bin independently and propagate the errors in the flux time series to amplitude uncertainty.
The amplitude spectrum ($A$ as a function of wavelength) of 2MASS J0835, (Figure \ref{fig:ampspec0835}), shows small ($\lesssim 0.4\%$) amplitudes with a flat trend as a function of wavelength.
2MASS J1821, on the other hand, shows a clear decreasing trend as function of wavelength.
This is the same trend observed for 2MASS J1821 by HST over a shorter wavelength range (1.1 to 1.7~$\mu$m) by \citet{yang2016exStormsBD}.
We shade the regions from 1.32 to 1.5~$\mu$m and 1.78 to 1.95~$\mu$m in Figure \ref{fig:ampSpec} because these wavelength ranges are affected by telluric water vapor absorption not fully removed by the simultaneous reference star.

@@

\section{Color-Magnitude Diagram}
\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{color_mag.pdf}
\caption{Color-Magnitude diagram from \citet{dupuy2012ltparallax}. We added 2MASS J1821 and 2MASS J0835 using Simbad magnitudes and parallaxes.}\label{fig:CMD}
\end{centering}
\end{figure}
